---
title: "Wet Weights for DEB"
author: "Teresa G. Schwemmer"
date: "10/4/2021"
output: html_document
---

The purpose of this script is to calculate the means, standard errors, and sample sizes of the wet weight data on 122 dph *Menidia menidia* from Murray et al (2017, *ICES Journal of Marine Science*). The paper contains the means by treatment but I also wanted to see the standard error and sample sizes, and separate it by tank to see the differences between tanks. 

Import the data from bco-dmo.org and make sure the relevant variables are the right data type. I want CO2_treatment and tank to be factors with two and four levels, respectively, and wet_weight to be numeric.
```{r}
wetwt<-read.csv(file.choose(),header=TRUE)
str(wetwt)

wetwt$CO2_treatment<-factor(wetwt$CO2_treatment,levels=c("500","2150"))
wetwt$tank<-factor(wetwt$tank,levels=c("A","B","C","D"))
wetwt$wet_weight<-as.numeric(wetwt$wet_weight)

str(wetwt)

```

Create summary tables of means, standard errors, and sample sizes for each treatment. Then repeat for each tank. The means should match the means reported in the paper if this code worked right. 
```{r}
library(plyr)
treatmentsummary<-ddply(wetwt,"CO2_treatment",summarise,MeanWW=mean(wet_weight),StErr=sd(wet_weight)/sqrt(length(wet_weight)),N=length(wet_weight))
treatmentsummary

tanksummary<-ddply(wetwt,"tank",summarise,MeanWW=mean(wet_weight),StErr=sd(wet_weight)/sqrt(length(wet_weight)),N=length(wet_weight))
tanksummary

```

**References**

Murray, C. S., L. A. Fuiman, and H. Baumann. 2017. Consequences of elevated CO2 exposure across multiple life stages in a coastal forage fish. *ICES Journal of Marine Science.* 74(4), 1051-1061. 

Baumann, H., Nye, J. (2016) Laboratory study of long-term growth in juvenile Menidia menidia (Atlantic silverside) at contrasting CO2 levels for 16 to 122 days in 2015. Biological and Chemical Oceanography Data Management Office (BCO-DMO). (Version final) Version Date 2016-07-07. doi:10.1575/1912/bco-dmo.652124 [accessed 2021-04-10]. 